---
title: "Scooby-Doo"
author: "Sara Knight, Alexa Kraklau"
date: "2/23/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, include=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(readr)
library(extrafont)
library(infer)

```


In this course, we will:

**Import, manage, and clean data.**

```{r load_data, include=FALSE}

scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')

```


```{r for side by side bar graph}

caught_captured<-scoobydoo %>% 
  select(caught_fred:captured_scooby) %>% 
  pivot_longer(cols = everything(),
               names_to = c("action","character"),
               names_pattern = "(.*)_(.*)",
               values_to = "yes") %>% 
  filter(yes == "TRUE")

```


```{r}
scoobydoo_tv <- scoobydoo %>% 
  filter(format == "TV Series")

scoobydoo_tv_segmented <- scoobydoo %>% 
  filter(format == "TV Series (segmented)")

scoobydoo_crossover <- scoobydoo %>%
  filter(format == "Crossover")

scoobydoo_movie <- scoobydoo %>% 
  filter(format == "Movie")
```

```{r filter_out_different_show}
scoobydoo_where_are_you <- scoobydoo %>% 
  filter(series_name == "Scooby Doo, Where Are You!")
scoobydoo_the_new_scoobydoo_movies <- scoobydoo_tv %>% 
  filter(series_name == "The New Scooby-Doo Movies")
the_scoobydoo_show <- scoobydoo %>% 
  filter(series_name == "The Scooby-Doo Show" )
scoobydoo_and_scrappydoo <- scoobydoo %>% 
  filter(series_name == "Scooby-Doo and Scrappy-Doo (first series)")
new_scoobydoo_and_scrappydoo_show <- scoobydoo %>% 
  filter(series_name == "The New Scooby and Scrappy Doo Show")

```




**Create graphical displays and numerical summaries of data for exploratory analysis and presentations.**

```{r side by side bar graph}
boxplot1 <- ggplot(data = caught_captured, aes(x = character, fill = action)) +
  geom_bar(stat = "count", position = position_dodge(), alpha = 1,) + 
  scale_fill_manual(values=c("captured" = "#00CFD4",
                             "caught" = "#00E304"))


boxplot1 <- boxplot1 + labs(title = "Captured versus Caught for Each Character",
              subtitle = "Comparison of amount of episodes each character was \ncaptured by monster versus catching the monster",
              x = "Characters", y = "Number of Episodes",
              fill="Action",
              tag = "1") + theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5)) +
  theme(text=element_text(size=10,  family="Times New Roman", color= "blue" ))

boxplot1
```
**Write R programs for simulations from probability models and randomization-based experiments.**

```{r bootstrapping}
scooby_tv_tidy <- scoobydoo_tv %>% 
  select(index, imdb) %>% 
  filter( imdb != "NULL")

scooby_sample <- scooby_tv_tidy %>% 
  rep_sample_n(size = 50, replace = TRUE, reps = 1000)

scooby_sample <- as.data.frame(apply(scooby_sample, 2, as.numeric)) 

scoobyboot <- scooby_sample %>% 
  group_by(index) %>% 
  summarize(mean_imdb = mean(imdb))

scoobyboot
```

```{r graph bootstrapping}

ggplot(scoobyboot, aes(x = mean_imdb)) +
  geom_histogram(binwidth = .1, color = scooby_gang_colors("Fred Blue"), fill = scooby_gang_colors("Fred Orange")) +
  labs(title = "Distribution of Sample Means from 1000 Resamples", x = "Sampled Mean IMDB", y = "Count", tag = "3")+
  theme(plot.title = element_text(hjust = 0.5))

```

**Use source documentation and other resources to troubleshoot and extend R programs.**


**Write clear, efficient, and well-documented R programs.**

Trying to create a color palette for our project
```{r colors}
 scooby_gang_colors <- function(...) {
   palette <- c(`Shaggy Green` = "#B8B#19",
                   `Shaggy Red Brown` ="#A44138",
                   `Velma Orange` = "#F8991D",
                   `Velma Red` = "#C70C47",
                   `Daphne Green` = "#D0D61B",
                   `Daphne Dark Purple` = "#6352A3",
                   `Scooby Brown` = "#6A3400",
                   `Scooby Blue` = "#7BDB9",
                   `Fred Blue` ="#009DDC",
                   `Fred Orange`= "#F47920",
                   `Mystery Machine Green` = "#00CFD4", 
                   `Mystery Machine Blue` ="#00E304")
  cols <-c(...)
  
  if (is.null(cols))
    return(palette)
  
  palette[cols]
}
#scooby_gang_colors("Shaggy Green")
```
https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2


This is my attempt a looking at all the places Mystery Inc has been.

Here I filter the data in order to make a smaller data frame. Then I changed
data points points so I could join this data fram with another. Finally I 
filtered out the data points that weren't useful to making my map.

This is also an example of creating a graphical display of the world with a 
gradient of how many episodes were in the country.
```{r}
scoobydoo_earth <- scoobydoo %>% 
  select(setting_country_state)
scoobydoo_earth[scoobydoo_earth == "United States"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Arizona"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "California"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Colorado"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Florida"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Georgia"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Hawaii"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Illinois"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Kentucky"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Kentukey"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Alaska"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Louisiana"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Massachusetts"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Mississippi"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Missouri"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Nevada"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New Jersey"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New Mexico"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "New York"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "North Carolina"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Pennsylvania"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Ohio"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Rhode Island"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Tennessee"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Texas"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Vermont"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Washington"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Washington D.C."] <- "USA"
scoobydoo_earth[scoobydoo_earth == "Wisconsin"] <- "USA"
scoobydoo_earth[scoobydoo_earth == "England"] <- "UK"
scoobydoo_earth[scoobydoo_earth == "Scotland"] <- "UK"
scoobydoo_earth[scoobydoo_earth == "Hong Kong"] <- "China"
scoobydoo_earth[scoobydoo_earth == "Siam"] <- "Thailand"
scoobydoo_earth <- scoobydoo_earth %>% 
  group_by(setting_country_state) %>% 
  summarise(num_of_episodes = n()) %>% 
  select(setting_country_state, num_of_episodes) %>% 
  filter(setting_country_state != "Atlantis") %>% 
  filter(setting_country_state != "Bermuda Triangle") %>% 
  filter(setting_country_state != "Indian Reserve") %>%  # Too vague
  filter(setting_country_state != "Mars") %>% 
  filter(setting_country_state != "Moon") %>% 
  filter(setting_country_state != "Pre-Historic") %>% 
  filter(setting_country_state != "Space") %>% 
  filter(setting_country_state != "Africa") %>% # Africa is a continent
  filter(setting_country_state != "Caribean") %>% # Caribean is part of many countries
  filter(setting_country_state != "South America") %>% #South America is a continent
  filter(setting_country_state != "Tibet") #I don't know enough about the history of Tibet
  
names(scoobydoo_earth)[names(scoobydoo_earth) == "setting_country_state"] <- "region"
mapdata <- map_data("world")
mapdata <-left_join(mapdata, scoobydoo_earth, by = "region")
#mapdata1 <- mapdata %>% filter(!is.na(mapdata$num_of_episodes)) This was making it so I couldn't see all the countries and commenting it out fixed it.
map1 <- ggplot(mapdata, aes(x = long, y = lat, group = group))+
  geom_polygon(aes(fill = num_of_episodes), color = "black")
map1
scoobydoo_world_map <- map1 + scale_fill_gradient(name = "Number of Episodes", low = scooby_gang_colors("Mystery Machine Blue"), high = scooby_gang_colors("Mystery Machine Green"), na.value = "gray")+
  labs(title = "Mystery Inc Traveling Around the World",
       caption = "Excluded Places inclued: Atlantis, Bermuda Triangle, Mars, Moon, Pre-Historic, and Space", tag = "2")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      rect = element_blank())
scoobydoo_world_map
#This was an attempt to figure out where the two data frames weren't matching up
#in_scooby_not_in_real_world <- anti_join(scoobydoo_earth, mapdata, by = "region")
```


```{r catchphrases}
scoobydoo_cp <- scoobydoo %>% 
  select("another_mystery", "jeepers", "jinkies", "my_glasses", "zoinks","groovy","rooby_rooby_roo")
scoobydoo_cp[scoobydoo_cp == "NULL"] <- "0"
scoobydoo_cp[] <- lapply(scoobydoo_cp, as.numeric)
fred <- sum(scoobydoo_cp$another_mystery) 
daphne <- sum(scoobydoo_cp$jeepers)
velma1 <- sum(scoobydoo_cp$jinkies)
velma2 <- sum(scoobydoo_cp$my_glasses)
shaggy1 <- sum(scoobydoo_cp$zoinks)
shaggy2 <- sum(scoobydoo_cp$groovy)
scooby <- sum(scoobydoo_cp$rooby_rooby_roo)
velma <- sum(velma1,velma2)
shaggy <- sum(shaggy1,shaggy2)
character <- c("Fred", "Daphne", "Velma", "Shaggy", "Scooby")
catch_phrase <- c(fred, daphne, velma, shaggy, scooby)
gang_cp <- data.frame(character, catch_phrase)
ggplot(data = gang_cp)+
  geom_bar(mapping = aes(x = character, y = catch_phrase), stat = "identity")+
  scale_fill_manual(values =c("Fred" = scooby_gang_colors("Fred Blue"),
                              "Daphne" = scooby_gang_colors("Daphne Purple"),
                              "Velma" = scooby_gang_colors("Velma Orange"),
                              "Shaggy" =scooby_gang_colors("Shaggy Green"),
                              "Scooby" = scooby_gang_colors("Scooby Brown")))
```


